\begin{problem}{Global Solidarity}{standard input}{standard output}{1 second}{256 megabytes}

Across the world, protests are held daily in support of Palestine. Cities from Tunisia to Europe and beyond organize coordinated demonstrations to \textbf{raise awareness, provide support, and pressure for justice.}

Consider $n$ key protest actions, each labeled from $1$ to $n$, representing strategic events or campaigns. Currently, the order of attention and resources is given by a permutation†$A$, but global organizers want to align the actions into a target configuration $B$ to maximize impact and ensure that solidarity remains strong.

You may perform the following operation any number of times (\emph{possibly zero}):

\begin{itemize}
  \item Choose four \emph{pairwise distinct} indices $i,j,k,l$ (that is, $i,j,k,l$ are \textbf{all different}).
  \item Then perform \textbf{simultaneously} the two swaps
    $$\text{swap}\bigl(A[i],A[k]\bigr)\quad\text{and}\quad \text{swap}\bigl(A[j],A[l]\bigr).$$
\end{itemize}

Determine the \textbf{minimum} number of such operations required to transform $A$ into $B$, or print $-1$ if it is impossible.

†
 A permutation is an array consisting of $n$ distinct integers from $1$ to $n$ in arbitrary order. For example, $[2,3,1,5,4]$ is a permutation, but $[1,2,2]$ is not a permutation ($2$ appears twice in the array), and $[1,3,4]$ is also not a permutation ($n=3$ but there is $4$ in the array).

\InputFile
The first line contains a single integer $t$ $(1 \le t \le 4\cdot 10^5)$ --- the number of test cases.

The first line of each test case contains an integer $n$ $(1 \le n \le 2\cdot 10^5)$--- the length of the arrays $A$ and $B$.

The second line of each test case contains $n$ integers $A_1,A_2,\dots,A_n$ --- the array $A$.

The third line of each test case contains $n$ integers $B_1,B_2,\dots,B_n$ --- the array $B$.

It is guaranteed that both $A$ and $B$ are permutations of $\{1,\dots,n\}$.

It is guaranteed that the sum of $n$ over all test cases does not exceed $4\cdot 10^5$ .

\OutputFile
Print a single integer --- the minimum number of allowed operations required to make $A$ equal to $B$, or $-1$ if it is impossible.

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\end{problem}

